---
title: "Workflow for reconstructing fish community size and trophic structure datasets from French river surveys using {targets}"
author: "Fellows of the Fish Food Webs - F<sup>3</sup>W"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 3
    number_sections: true
    css: styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# **Objectives**

This vignette presents a reproducible workflow for reconstructing fish community size and trophic structure datasets from French river surveys. It combines `{fishdatabuilder}` and `{foodwebbuilder}` within a `{targets}` pipeline.

The workflow comprises two main components:
- generating a standardised individual fish body-size dataset from ASPE electrofishing surveyss (***doi:*** [10.1051/kmae/2022021](https://doi.org/10.1051/kmae/2022021));
- reconstructing a metaweb from individual fish body-size data, species identity, ontogenetic diet information and predator–prey body-size windows, then deriving local food webs and their associated metrics from local fish community composition.

---

# **Project setup**

## ***Install the required packages***

Install the required CRAN packages before running the workflow.

```{r install-packages, eval=FALSE}
install.packages(
  c(
    "targets",
    "tarchetypes",
    "pkgfilecache",
    "dplyr",
    "tidyr",
    "purrr",
    "tibble",
    "stringr",
    "pak",
    "kableExtra",
    "rfishbase"
  )
)

pak::pak("Fellows-of-the-Fish-Food-Webs-F3W/fishdatabuilder")
pak::pak("Fellows-of-the-Fish-Food-Webs-F3W/foodwebbuilder")
```

## ***Initialise Target Markdown***

This document uses Target Markdown. The `{targets}` chunks defined in the R Markdown file are used to generate the `_targets.R` script automatically.
Before knitting the document for the first time, rename, move or remove any `_targets.R` file that was written manually. For example, it can be renamed `_targets_backup.R`. Otherwise, `{tarchetypes}` will refuse to overwrite it.

```{r initialise-project}
library(targets)
library(tarchetypes)

tar_unscript()
```

---

# **Pipeline configuration**

The following chunk defines the global options and packages required when the targets are executed. Because `tar_globals = TRUE`, the objects created in this chunk are made available throughout the pipeline.
By default, the `imports` argument is omitted to keep the dependency graph generated by `tar_visnetwork()` in the **Generate and run the pipeline** section concise and focused on data targets. If you wish to display the functions from the `{fishdatabuilder}` and `{foodwebbuilder}` packages, simply uncomment the `imports` argument in `tar_option_set()`. This will add these package functions as nodes in the dependency graph.

```{targets pipeline-configuration, tar_globals=TRUE}
options(tidyverse.quiet = TRUE)

library(pkgfilecache)
library(stringr)
library(dplyr)
library(tidyr)
library(purrr)
library(tibble)
library(kableExtra)
library(rfishbase)
library(fishdatabuilder)
library(foodwebbuilder)

tar_option_set(
  packages = c(
    "pkgfilecache",
    "stringr",
    "dplyr",
    "tidyr",
    "purrr",
    "tibble",
    "kableExtra",
    "rfishbase",
    "fishdatabuilder",
    "foodwebbuilder"
  )#,
  #imports = c(
  #  "fishdatabuilder",
  #  "foodwebbuilder"
  #)
)
```

The following sections describe the main stages of the workflow. Each processing step is stored as a `{targets}` object, allowing intermediate results to be cached and only outdated targets to be recomputed.

---

# **Step 1 - Import ASPE survey data**

The workflow begins by importing the raw tables describing fish sampling operations from the ASPE database.

The `{fishdatabuilder}` package provides accessor functions named `get_*()` that retrieve these tables from a local package cache. Source files are downloaded from Zenodo when first requested and are subsequently reused through `{pkgfilecache}`.

The files available through the package cache can be inspected with:

```{r list-optional-files, eval=FALSE}
list_optional_files()
```

Each table required by the workflow is imported as a separate target.

```{targets import-sampling-data}
list(
  # Table containing fishing operation data.
  tar_target(
    operation,
    get_raw_operation_aspe() |>
      as_tibble()
  ),
  # Table containing operation objective reference data.
  tar_target(
    ref_objective,
    get_ref_objective_operation_aspe() |>
      as_tibble()
  ),
  # Table containing sampling protocol reference data.
  tar_target(
    ref_protocol,
    get_ref_protocol_operation_aspe() |>
      as_tibble()
  ),
  # Table containing ref_objective-ref_protocol relationship data.
  tar_target(
    operation_objective,
    get_objective_operation_aspe() |>
      as_tibble()
  ),
  # Table containing sampling point location data.
  tar_target(
    sampling_point,
    get_sampling_point_aspe() |>
      as_tibble()
  ),
  # Table containing detailed fishing operation descriptions.
  tar_target(
    operation_description,
    get_description_operation_aspe() |>
      as_tibble()
  ),
  # Table containing barrier isolation type reference data.
  tar_target(
    ref_isolation,
    get_ref_isolation_operation_aspe() |>
      as_tibble()
  ),
  # Table containing detailed fishing sampling protocol.
  tar_target(
    elementary_sampling,
    get_elementary_sampling_aspe() |>
      as_tibble()
  ),
  # Table containing elementary sampling type reference data.
  tar_target(
    ref_elementary_sampling,
    get_ref_elementary_sampling_aspe() |>
      as_tibble()
  ),
  # Table containing prospection method reference data.
  tar_target(
    ref_prospection_method,
    get_ref_prospection_method_operation_aspe() |>
      as_tibble()
  ),
  # Table containing references for passage sampling protocol, including the number of passage.
  tar_target(
    ref_passage,
    get_ref_passage_aspe() |>
      as_tibble()
  ),
  # Table containing point sampling.
  tar_target(
    point_group,
    get_point_group_aspe() |>
      as_tibble()
  ),
  # Table containing references for point group sampling protocol, such as sampling points from the bank and the channel.
  tar_target(
    ref_point_group,
    get_ref_point_group_aspe() |>
      as_tibble()
  ),
   # Table containing the different types of fish batches.
  tar_target(
    ref_batch_type,
    get_ref_type_batch_aspe() |>
      as_tibble()
  ),
  # Table containing fish batches recorded during sampling operations.
  tar_target(
    fish_batch,
    get_fish_batch_aspe() |>
      as_tibble()
  ),
  # Table containing individual measurement of fishes.
  tar_target(
    individual_measurement,
    get_individual_measurement_aspe() |>
      as_tibble()
  ),
  # Table containing method of length measurement.
  tar_target(
    ref_length_type,
    get_ref_type_length_aspe() |>
      as_tibble()
  ),
  # Table containing ASPE species reference containing species names and taxonomic identifiers.
  tar_target(
    ref_species,
    get_species_aspe() |>
      as_tibble()
  )
)
```

The imported tables are summarised below.

| Name                      | Content                                           |
| ------------------------- | ------------------------------------------------- |
| `operation`               | Fishing operation data                            |
| `ref_objective`           | Operation objective reference data                |
| `ref_protocol`            | Sampling protocol reference data                  |
| `operation_objective`     | Relationships between operations and objectives   |
| `sampling_point`          | Sampling point location data                      |
| `operation_description`   | Detailed fishing operation descriptions           |
| `ref_isolation`           | Barrier isolation type reference data             |
| `elementary_sampling`     | Detailed fishing sampling protocol                |
| `ref_elementary_sampling` | Reference data for the fishing sampling protocol  |
| `ref_prospection_method`  | Prospection method reference data                 |
| `ref_passage`             | Reference data for sampling passages              |
| `point_group`             | Point sampling data                               |
| `ref_point_group`         | Reference data for point-group sampling protocols |
| `ref_batch_type`          | Fish batch type reference data                    |
| `fish_batch`              | Sampled fish batches                              |
| `individual_measurement`  | Individual fish measurements                      |
| `ref_length_type`         | Length measurement type reference data            |
| `ref_species`             | ASPE species reference data                       |

---

# **Step 2 - Clean and harmonise ASPE tables**

The raw ASPE tables cannot be used directly to reconstruct the size and trophic structure of fish communities. Variable names, identifiers and reference tables must first be harmonised into a consistent format.

The `{fishdatabuilder}` package provides a collection of cleaning functions that standardise these tables and prepare them for downstream analyses.

```{targets cleaning-data}
list(
  # Standardised species reference data.
  tar_target(
    ref_species_clean,
    cleaning_species_ref_aspe(species = ref_species)
  ),
  # Standardised body-length reference data.
  tar_target(
    ref_length_type_clean,
    cleaning_ref_length_type_aspe(ref_length = ref_length_type)
  ),
  # Cleaned fishing operations.
  tar_target(
    operation_clean,
    clean_operation_aspe(op = operation,
                         op_objective = operation_objective,
                         ref_objective = ref_objective,
                         ref_protocol = ref_protocol,
                         sampling_point = sampling_point)
  ),
  # Cleaned elementary sampling data.
  tar_target(
    elementary_sampling_clean,
    cleaning_elementary_sampling(sampling = elementary_sampling,
                                 ref_sampling = ref_elementary_sampling,
                                 ref_passage = ref_passage)
  ),
  # Cleaned point-group sampling data.
  tar_target(
    point_group_clean,
    cleaning_point_group(point_group = point_group,
                         ref_point_group = ref_point_group)
  ),
  # Cleaned fish batch types.
  tar_target(
    ref_batch_type_clean,
    cleaning_ref_batch_type_aspe(ref_batch = ref_batch_type)
    ),
  # Cleaned fish-batch data.
  tar_target(
    fish_batch_clean,
    clean_fish_batch(fish_batch = fish_batch,
                     batch_ref = ref_batch_type_clean,
                     species_ref = ref_species_clean,
                     length_ref = ref_length_type_clean,
                     detail_sampling = elementary_sampling_clean)
  ),
  # Cleaned individual fish measurements.
  tar_target(
    individual_measurement_clean,
    clean_individual_measurement_aspe(ind_measure = individual_measurement,
                                      fish_batch = fish_batch_clean,
                                      op = operation_clean)
  )
)
```

The imported and cleaned tables are summarised below.

| Raw table                | Cleaned table                  |
|:-------------------------|:-------------------------------|
| `ref_species`            | `ref_species_clean`            |
| `ref_length_type`        | `ref_length_type_clean`        |
| `ref_batch_type`         | `ref_batch_type_clean`         |
| `operation`              | `operation_clean`              |
| `elementary_sampling`    | `elementary_sampling_clean`    |
| `point_group`            | `point_group_clean`            |
| `fish_batch`             | `fish_batch_clean`             |
| `individual_measurement` | `individual_measurement_clean` |

---

# **Step 3 - Filter sampling operations and associated fish data**

Sampling operations and their associated fish data are filtered to produce a consistent dataset for fish community size and trophic analyses.Fish batches and individual measurements associated with excluded sampling operations are removed simultaneously to maintain consistency among datasets.
Species codes are also standardised in the retained fish-batch and individual-measurement tables by removing unwanted taxa and harmonising undetermined or hybrid codes.

The resulting `filtered_sampling` target is a named list containing three mutually consistent tables:
* `operation`: retained sampling operations;
* `fish_batch`: fish batches associated with the retained operations;
* `ind_measure`: individual fish measurements associated with the retained batches.

```{targets filter-sampling-data}
tar_target(
  filtered_sampling,
  {
    filtered_data <- filter_operation_batch_measure(
      operation = operation_clean,
      op_protocol_to_keep = c(
        "complete",
        "partial_by_point",
        "partial_over_bank"
      ),
      op_objective_to_exclude = vec_op_objective_to_exclude(ref_protocol = ref_objective),
      oldest_sampling_date = "1995-01-01",
      omit_na_site = TRUE,
      point_group = point_group_clean,
      min_prop_point_group_on_bank = 0.999,
      ele_sampling = elementary_sampling_clean,
      max_passage_number = 1,
      fish_batch = fish_batch_clean,
      ind_measure = individual_measurement_clean
    )

    filtered_data[c("fish_batch", "ind_measure")] <-
      filtered_data[c("fish_batch", "ind_measure")] |>
      purrr::map(
        \(x) sanitize_species_code(
          data = x,
          species_ref = ref_species_clean
        )
      )

    filtered_data
  }
)
```

---

# **Step 4 - Generate individual fish body-size data**

Fish body-size information is recorded at different levels in the ASPE database. During field sampling, individuals are sorted into species-specific batches according to their body size. Four batch types are distinguished (N, I, S/L and G): N and I batches contain individually measured fish, S/L batches include measurements for a subsample of individuals, whereas G batches are described only by their minimum and maximum body lengths. Body length may also be reported either as total length or fork length.

This step transforms these heterogeneous records into a consistent individual-level body-size dataset suitable for fish community size and trophic analyses. To achieve this, length measurements not already recorded as total length are converted to total length, biologically implausible observations are removed, fish batches are validated according to batch-specific quality criteria, and missing individual body sizes are inferred from batch-level information.

The procedure comprises five successive operations:

1. identification of species recorded using fork-length measurements and retrieval of species-specific length-conversion relationships from FishBase;
2. conversion of fork lengths to total lengths;
3. removal of measurements exceeding species-specific maximum body lengths;
4. validation of fish batches against batch-type quality criteria;
5. inference of individual fish sizes for all retained batches.

```{targets prepare-individual-fish-sizes}
list(
  # Identify species for which at least one batch was measured in fork length.
  # Species names are used to retrieve the conversion relationships from FishBase in the following target.
  tar_target(
    species_fork_length,
    filtered_sampling$fish_batch |>
      dplyr::filter(length_type == "fork") |>
      dplyr::distinct(species_code) |>
      dplyr::left_join(
        ref_species_clean,
        by = dplyr::join_by(species_code)
      )
  ),
  # Retrieve species-specific relationships required to convert fork length to total length.
  # Species without a valid Latin name are excluded from the FishBase query.
  tar_target(
    fishbase_length_relationships,
    rfishbase::length_length(
      species_list = species_fork_length$latin_name |>
        stats::na.omit() |>
        unique()
    )
  ),
  # Convert fork-length measurements to total length using species-specific relationships.
  #FishBase coefficients are used whenever available, whereas manually curated coefficients are used for species
  #lacking a suitable FishBase relationship.
  tar_target(
    length_type_standardised,
    convert_fork_to_total(
      fish_batch = filtered_sampling$fish_batch,
      ind_measure = filtered_sampling$ind_measure,
      species_ref = ref_species_clean,
      fishbase_length_length = fishbase_length_relationships,
      conversion_vector = coefficients_fork2total(),
      convert_intercept_cm2mm = TRUE,
      manual_priority = FALSE,
      verbose = TRUE
    )
  ),
  # Remove biologically implausible body lengths by comparing individual and
  # batch-level measurements with species-specific maximum body lengths.
  # Records exceeding these limits are discarded.
  tar_target(
    length_data_validated,
    remove_impossible_lengths(
      ind_measure = length_type_standardised$ind_measure,
      fish_batch = length_type_standardised$fish_batch,
      species_ref = ref_species_clean,
      remove_outliers = TRUE
    )
  ),
  # Apply batch-type quality criteria before generating individual body sizes.
  # Batches that do not satisfy these criteria are removed together with their associated measurements.
  tar_target(
    batch_data_validated,
    sanitize_batch_data(
      fish_batch = length_data_validated$fish_batch,
      ind_measure = length_data_validated$ind_measure,
      species_ref = ref_species_clean,
      min_individuals_G = 2,
      min_individuals_SL = 6,
      verbose = TRUE
    )
  ),
  # Generate a complete individual-level body-size dataset by retaining observed individual measurements
  # and inferring missing individual body sizes from batch-level information.
  tar_target(
    fish_individual_size,
    generate_individual_sizes(
      sanitized = batch_data_validated,
      seed = 123L,
      verbose = TRUE
    )
  )
)
```

The final `fish_individual_size` target contains one record per individual fish. It combines directly measured body lengths with sizes inferred from batch-level information. The dataset therefore provides a consistent individual-level representation of fish body size, expressed as total length, for all sampling operations retained in the previous step.

---

# **Step 5 - Build the trophic metaweb**

This step builds a trophic metaweb representing all potential trophic interactions among the fish species and resources considered. Individual fish are first grouped into species-specific size classes, after which potential interactions are determined from species identity, body size, ontogenetic diet information and predator–prey body-size windows

```{targets build-trophic-metaweb}
# Set of resource nodes that can be included in the trophic networks.
selected_resources <- c(
  "det", #detritus
  "biof", #biofilm
  "phytob", #phytobenthos
  "macroph", #macrophytes
  "phytopl", #phytoplankton
  "zoopl", #zooplankton
  "zoob" #zoobenthos
)

list(
  # Remove species lacking the information required to reconstruct
  # trophic interactions and standardise the body-size column.
  tar_target(
    fish_individual_size_filtered,
    remove_missing_species(
      ind_measure = fish_individual_size,
      fish_diet_shift = fish_diet_shift,
      pred_win = pred_win
    )
  ),
  # Divide the observed body-size range of each species into
  # a predefined number of size classes.
  tar_target(
    size_classes,
    compute_size_classes(
      ind_measure = fish_individual_size_filtered,
      num_classes = 9
    )
  ),
  # Build the size-structured trophic metaweb by combining
  # size classes, ontogenetic diet shifts and predator-prey
  # size constraints.
  tar_target(
    trophic_metaweb,
    build_metaweb(
      tab_size_classes = size_classes,
      pred_win = pred_win,
      fish_diet_shift = fish_diet_shift,
      resource_diet_shift = resource_diet_shift,
      selected_resources = selected_resources
      )
    )
  )
```

---

# **Step 6 - Reconstruct local food webs**

This step reconstructs local food-webs for each sampling operation. The metaweb is restricted to the fish species and size classes observed locally, while retaining always the selected resource nodes.

```{targets build-local-food-webs}
tar_target(
  local_foodwebs,
  build_local_foodweb(
    ind_measure = fish_individual_size_filtered,
    local_id = "operation_id",
    metaweb = trophic_metaweb,
    tab_size_classes = size_classes,
    selected_resources = selected_resources
    )
  )
```

---

# **Step 7 - Compute food-web metrics**

This step computes summary network metrics for each reconstructed local food-web. The resulting table contains one row per sampling operation and the food-web metrics returned by `compute_metrics_summary()`.

```{targets compute-food-web-metrics}
tar_target(
  local_foodweb_summary_metrics,
  purrr::imap_dfr(
    local_foodwebs,
    function(local_foodweb, operation_id) {
      metrics <- compute_metrics_summary(local_foodweb)

      tibble::as_tibble_row(
        c(
          operation_id = operation_id,
          metrics
        )
      )
    }
  )
)
```
---

# **Generate and run the pipeline**

If all `{targets}` chunks were run in non-interactive mode, the R scripts required to run the pipeline have been generated.

```{r run-pipeline, message=FALSE, warning=FALSE, results='hide'}
tar_make(
  envir = parent.frame()
)
```

To identify targets that need to be rebuilt, the outdated targets can be listed as follows:

```{r outdated-targets, message=FALSE, warning=FALSE, results='hide'}
tar_outdated()
```

The dependency graph of the pipeline can be visualised as follows:

```{r pipeline-graph, message=FALSE, warning=FALSE, out.width='100%'}
tar_visnetwork( callr_function = NULL )
```

---

# **Inspect pipeline outputs**

Once the pipeline has been executed with `tar_make()`, you can retrieve results from the `_targets/` data store using `tar_read()` or `tar_load()`.

## ***Compare datasets across workflow stages***

The following table summarises changes in dataset dimensions across the successive data-processing stages, from raw ASPE tables to the individual-level body-size dataset used for food-web reconstruction.

```{r compare-datasets-across-workflow-stages, echo=FALSE, message=FALSE, warning=FALSE}
targets_to_load <- c(
  "ref_species",
  "ref_species_clean",
  "ref_length_type",
  "ref_length_type_clean",
  "ref_batch_type",
  "ref_batch_type_clean",
  "operation",
  "operation_clean",
  "elementary_sampling",
  "elementary_sampling_clean",
  "point_group",
  "point_group_clean",
  "fish_batch",
  "fish_batch_clean",
  "individual_measurement",
  "individual_measurement_clean",
  "filtered_sampling",
  "length_type_standardised",
  "length_data_validated",
  "batch_data_validated",
  "fish_individual_size",
  "fish_individual_size_filtered"
)

targets::tar_load(
  tidyselect::all_of(targets_to_load)
)

comparison <- tibble::tribble(
  ~Dataset,                        ~Stage,                          ~Data,
  "Species reference",            "Raw",                           ref_species,
  "Species reference",            "Cleaned",                       ref_species_clean,

  "Length reference",             "Raw",                           ref_length_type,
  "Length reference",             "Cleaned",                       ref_length_type_clean,

  "Batch type reference",         "Raw",                           ref_batch_type,
  "Batch type reference",         "Cleaned",                       ref_batch_type_clean,

  "Fishing operations",           "Raw",                           operation,
  "Fishing operations",           "Cleaned",                       operation_clean,
  "Fishing operations",           "Filtered",                      filtered_sampling$operation,

  "Elementary sampling",          "Raw",                           elementary_sampling,
  "Elementary sampling",          "Cleaned",                       elementary_sampling_clean,

  "Point groups",                 "Raw",                           point_group,
  "Point groups",                 "Cleaned",                       point_group_clean,

  "Fish batches",                 "Raw",                           fish_batch,
  "Fish batches",                 "Cleaned",                       fish_batch_clean,
  "Fish batches",                 "Filtered",                      filtered_sampling$fish_batch,
  "Fish batches",                 "Length-type standardisation",   length_type_standardised$fish_batch,
  "Fish batches",                 "Length quality filtering",      length_data_validated$fish_batch,
  "Fish batches",                 "Batch-type quality filtering",  batch_data_validated$fish_batch,

  "Individual measurements",      "Raw",                           individual_measurement,
  "Individual measurements",      "Cleaned",                       individual_measurement_clean,
  "Individual measurements",      "Filtered",                      filtered_sampling$ind_measure,
  "Individual measurements",      "Length-type standardisation",   length_type_standardised$ind_measure,
  "Individual measurements",      "Length quality filtering",      length_data_validated$ind_measure,
  "Individual measurements",      "Batch-type quality filtering",  batch_data_validated$ind_measure,

  "Individual body-size dataset", "Body-size dataset",       fish_individual_size,
  "Individual body-size dataset", "Trophic-information filtering", fish_individual_size_filtered
) |>
  dplyr::mutate(
    Stage = factor(
      Stage,
      levels = c(
        "Raw",
        "Cleaned",
        "Filtered",
        "Length-type standardisation",
        "Length quality filtering",
        "Batch-type quality filtering",
        "Body-size dataset",
        "Trophic-information filtering"
      )
    ),
    `# Rows` = purrr::map_int(Data, nrow),
    `# Columns` = purrr::map_int(Data, ncol)
  ) |>
  dplyr::select(
    Dataset,
    Stage,
    `# Rows`,
    `# Columns`
  )

comparison |>
  knitr::kable(
    format = "html",
    caption = paste(
      "Comparison of ASPE datasets across the successive processing stages."
    ),
    align = c("l", "l", "r", "r"),
    escape = TRUE
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = c(
      "striped",
      "hover",
      "condensed",
      "responsive"
    ),
    full_width = TRUE,
    position = "center"
  ) |>
  kableExtra::column_spec(
    column = 1,
    bold = TRUE,
    width = "14em"
  ) |>
  kableExtra::column_spec(
    column = 2,
    width = "12em"
  ) |>
  kableExtra::collapse_rows(
    columns = 1,
    valign = "top"
  )
```

## ***Compare species richness across workflow stages***

The following table shows how the number of fish species changes across the successive data-processing stages, from raw ASPE tables to the individual-level body-size dataset used for food-web reconstruction.

```{r compare-species-richness-across-workflow-stages, echo=FALSE, message=FALSE, warning=FALSE}
species_comparison <- tibble::tribble(
  ~Dataset,                        ~Stage,                          ~Data,
  "Fish batches",                 "Cleaned",                       fish_batch_clean,
  "Fish batches",                 "Filtered",                      filtered_sampling$fish_batch,
  "Fish batches",                 "Length-type standardisation",   length_type_standardised$fish_batch,
  "Fish batches",                 "Length quality filtering",      length_data_validated$fish_batch,
  "Fish batches",                 "Batch-type quality filtering",  batch_data_validated$fish_batch,

  "Individual measurements",      "Cleaned",                       individual_measurement_clean,
  "Individual measurements",      "Filtered",                      filtered_sampling$ind_measure,
  "Individual measurements",      "Length-type standardisation",   length_type_standardised$ind_measure,
  "Individual measurements",      "Length quality filtering",      length_data_validated$ind_measure,
  "Individual measurements",      "Batch-type quality filtering",  batch_data_validated$ind_measure,

  "Individual body-size dataset", "Body-size dataset",             fish_individual_size,
  "Individual body-size dataset", "Trophic-information filtering", fish_individual_size_filtered
) |>
  dplyr::mutate(
    Stage = factor(
      Stage,
      levels = unique(Stage)
    ),
    `# Species` = purrr::map_int(
      Data,
      \(data) dplyr::n_distinct(
        data$species_code,
        na.rm = TRUE
      )
    )
  ) |>
  dplyr::select(
    Dataset,
    Stage,
    `# Species`
  )

species_comparison |>
  knitr::kable(
    format = "html",
    caption = paste(
      "Number of fish species represented across the successive",
      "processing stages."
    ),
    align = c("l", "l", "r"),
    escape = TRUE
  ) |>
  kableExtra::kable_styling(
    bootstrap_options = c(
      "striped",
      "hover",
      "condensed",
      "responsive"
    ),
    full_width = TRUE,
    position = "center"
  ) |>
  kableExtra::column_spec(
    column = 1,
    bold = TRUE,
    width = "14em"
  ) |>
  kableExtra::column_spec(
    column = 2,
    width = "12em"
  ) |>
  kableExtra::collapse_rows(
    columns = 1,
    valign = "top"
  )
```

---

# **Notes**

In this workflow, the R Markdown document is the source used to generate `_targets.R`. The generated `_targets.R` file should therefore not be edited manually. Any changes to the pipeline should instead be made in the corresponding `{targets}` chunks in this document.
For more information about Target Markdown and the generation of `_targets.R` from R Markdown documents, see the official `{targets}` documentation: https://books.ropensci.org/targets/markdown.html.
