---
title: "Example analysis of fish community size and trophic structure"
author: "Fellows of the Fish Food Webs - F3W"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example analysis of fish community size and trophic structure}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Overview

This vignette provides an initial worked example of the main `fish2webs`
workflow. It follows the analysis developed in
`dev/example-analysis-2026-08-20-1.R` and is intentionally kept close to that
script. The plotting code and its current formatting are retained.

The analysis covers:

- generation of cleaned individual fish size and weight data;
- exploration of sampling frequency and species abundance at a selected site;
- visualisation of fish-size distributions; and
- construction and visualisation of metawebs and local food webs.

The complete workflow can be computationally demanding because the survey data
and trophic information are loaded from the companion packages.

# Setup

```{r packages, message=FALSE}
library(fish2webs)
library(fishdatabuilder)
library(foodwebbuilder)
library(dplyr)
library(tibble)
```

The development analysis defines the following helper for plotting food webs.
It is reproduced here without changing its plotting parameters.

```{r plotting-helper, eval=FALSE}
plot_network <- function (M, x = NULL, y = NULL, labels = NULL, xlab = "", ylab = "",
                  line_width_max = 1, label_space_x = 0.05, add_legend = "topright",
                  cex.dots = 2, cex.text = 1.5)
{
  d = dim(M)[1]
  if (is.null(labels) == T)
    labels = 1:d
  if (is.null(x) == T)
    x = cos((1:d)/0.25)
  if (is.null(y) == T)
    y = sin((1:d)/0.25)
  delta_x = (max(x) - min(x)) * label_space_x
  plot(x, y, xlim = c(min(x) - delta_x, max(x) + delta_x * 1.5),
       cex = 0, bty = "n", xlab = xlab, ylab = ylab, cex.lab = 1.5,
       bty = "l")
  for (j in 1:ncol(M)) {
    color_ = rainbow(ncol(M))[j]
    for (i in 1:nrow(M)) {
      line_width = abs(M[i, j])/max(abs(M)) * line_width_max
      lines(x = c(x[i], x[j] - delta_x/2), y = c(y[i], y[j]),
            col = color_, lwd = line_width)
    }
  }
  points(x - delta_x/2, y, pch = 1, cex = cex.dots)
  points(x, y, pch = 16, cex = cex.dots)
  text(x + delta_x, y, labels = labels, cex = cex.text)
  if (add_legend != "off") {
    legend(add_legend, legend = c("Ingoing effects", "Outgoing effects"),
           pch = c(1, 16), col = c("black", "black"), cex = 1.5,
           bg = "white", box.col = "white")
  }
}
```

Load the trophic data required to construct the food webs.

```{r trophic-data}
data(resource_diet_shift, package = "foodwebbuilder")
data(fish_diet_shift, package = "foodwebbuilder")
data(pred_win, package = "foodwebbuilder")
```

# Generate fish size and weight data

`fish2size()` extracts and cleans the ASPE survey data, reconstructs individual
fish sizes where necessary, estimates body mass, and computes community- and
species-level metrics.

```{r fish2size, eval=FALSE}
fish_individual_size <- fish2size(write_output = FALSE)
```

The following object is used in the analyses below. The operation table is
joined to retain the site identifier for each individual fish record.

```{r prepare-data, eval=FALSE}
fish_data <- fish_individual_size$fish_individual_size_weight |>
  left_join(
    fish_individual_size$operation_information |>
      select(operation_id, site_id, date),
    by = "operation_id"
  )
```

# Sampling frequency across sites

The number of operations associated with each site can be joined to the site
coordinates and plotted as point sizes. This is the starting point for the
multi-site view used in the accompanying paper.

```{r sampling-frequency, eval=FALSE}
site_sampling_frequency <- fish_individual_size$operation_information |>
  distinct(operation_id, site_id) |>
  count(site_id, name = "n_operations") |>
  left_join(
    fish_individual_size$site_information,
    by = "site_id"
  )

plot(
  site_sampling_frequency$x,
  site_sampling_frequency$y,
  cex = site_sampling_frequency$n_operations,
  pch = 16,
  xlab = "x coordinate",
  ylab = "y coordinate"
)
```

# Single-site community patterns

For the exploratory analysis, select one site and retain all of its operations.
The index below follows the current development script and can be changed when
using the vignette.

```{r select-site, eval=FALSE}
site_id_ <- fish_data$site_id[9000]
site_fish_data <- fish_data[
  fish_data$site_id == site_id_,
]
```

## Species abundance through time

The following code counts individuals by species and operation, orders the
operations by date, and converts the counts to proportional abundance.

```{r abundance-time-series, eval=FALSE}
selected_species <- sort(unique(site_fish_data$species_code))
unique_op_ids <- unique(site_fish_data$operation_id)

res <- NULL
for (unique_op_ids_ in unique_op_ids) {
  site_fish_data_ <- site_fish_data[
    site_fish_data$operation_id == unique_op_ids_,
  ]
  res_ <- NULL
  for (selected_species_ in selected_species) {
    individual_count <- length(which(
      site_fish_data_$species_code == selected_species_
    ))
    res_ <- c(res_, individual_count)
  }
  res <- rbind(res, res_)
}

tab_species_abundances <- data.frame(res)
colnames(tab_species_abundances) <- selected_species

operation_dates <- fish_individual_size$operation_information |>
  filter(operation_id %in% unique_op_ids) |>
  distinct(operation_id, date)
times <- operation_dates$date[match(unique_op_ids, operation_dates$operation_id)]
times <- as.Date(times)
times <- as.numeric(times - min(times))
s <- order(times)
x <- times[s] / 365
y <- tab_species_abundances[s, ]
```

The stacked-area plot below retains the formatting used in the development
analysis.

```{r proportional-abundance-plot, eval=FALSE}
pdf(file = "plot-single-site-abundances.pdf", width = 5, height = 4)
par(mar = c(5, 5, 1, 1), xpd = TRUE, mfrow = c(1, 1), bty = "l")

sp <- selected_species
p <- as.matrix(y[, sp])
p <- p / rowSums(p)
cp <- t(apply(p, 1, cumsum))
plot(x, x,
     type = "n",
     ylim = c(0, 1),
     xlab = "Time (years)",
     ylab = "Proportion",
     axes = FALSE)
cols <- rainbow(length(sp), start = 0.0, end = 0.8, alpha = 0.75)
for (i in seq_along(sp)) {
  lower <- if (i == 1) rep(0, length(x)) else cp[, i - 1]
  upper <- cp[, i]
  polygon(c(x, rev(x)),
          c(lower, rev(upper)),
          col = cols[i],
          border = NA)
}
axis(1)
axis(2, las = 1)
box()
dev.off()
```

# Fish-size distributions

The following is the all-species size-distribution analysis from the
development script. Species can be restricted before this section when a
focused analysis is required.

```{r size-distributions, eval=FALSE}
d <- 4
unique_species_codes <- unique(fish_data$species_code)
xlim <- range(fish_data$size_mm, na.rm = TRUE)

par(
  mfrow = c(d, d),
  mar = c(3, 4, 2, 1),
  oma = c(2, 0, 2, 0)
)

for (i in seq_len(d^2)) {
  sizes <- fish_data[
    fish_data$species_code == unique_species_codes[i],
    "size_mm"
  ]

  hist(
    sizes,
    breaks = 20,
    xlim = xlim,
    col = "lightblue",
    border = "white",
    main = paste("Species:", unique_species_codes[i]),
    xlab = if (i == d) "Size (mm)" else "",
    ylab = "Count"
  )
}

mtext("Fish size distributions by species", outer = TRUE, cex = 1.4)
par(mfrow = c(1, 1))
```

## Total species counts

```{r species-counts, eval=FALSE}
pdf(file = "plot-single-site-counts.pdf", width = 2.5, height = 4)
par(mar = c(5, 5, 1, 1), xpd = TRUE, mfrow = c(1, 1), bty = "l")
res <- table(site_fish_data$species_code)
colors <- rainbow(length(res), start = 0.0, end = 0.8, alpha = 0.75)
barplot(res, horiz = TRUE, las = 1, col = colors,
        xlab = "Total count", cex.names = 0.7)
dev.off()
```

# Food webs

The food-web workflow assigns fish to species-specific size classes, builds a
global metaweb, and extracts local food webs for individual operations.

```{r size2webs, eval=FALSE}
web_outputs <- size2webs(
  num_classes = 9,
  ind_measure = fish_individual_size$fish_individual_size_weight,
  resource_diet_shift = resource_diet_shift,
  fish_diet_shift = fish_diet_shift,
  pred_win = pred_win,
  write_output = FALSE
)
```

## Global metaweb

```{r metaweb, eval=FALSE}
metaweb <- unflatten_foodweb(web_outputs$metaweb)
TL <- compute_trophic_level(metaweb)
TB <- compute_trophic_breadth(metaweb, TL)

plot_network(
  metaweb,
  x = TB,
  y = TL,
  labels = colnames(metaweb),
  xlab = "Trophic breadth (sd of resource TL)",
  ylab = "Trophic level",
  add_legend = "bottomright",
  label_space_x = 0.10
)
```

## Local food webs

One operation can be selected and its local food web reconstructed as follows.
The current development analysis repeats this procedure for operations through
time; two selected years can subsequently be passed to the same code when
assembling the paper figure.

```{r local-foodweb, eval=FALSE}
local_foodwebs <- web_outputs$local_foodwebs
operation_id_ <- unique(local_foodwebs$operation_id)[100]
local_foodweb_data <- local_foodwebs |>
  filter(operation_id == operation_id_) |>
  select(prey, consumer, interaction)
local_foodweb <- unflatten_foodweb(local_foodweb_data)

TL <- compute_trophic_level(local_foodweb)
TB <- compute_trophic_breadth(local_foodweb, TL)

plot_network(
  local_foodweb,
  x = TB,
  y = TL,
  labels = colnames(local_foodweb),
  xlab = "Trophic breadth (sd of resource TL)",
  ylab = "Trophic level",
  add_legend = "bottomright",
  label_space_x = 0.10
)
```

Resource nodes are part of the inferred network structure, but no empirical
fish biomass is available for them. They should therefore be assigned `NA`
when node biomass is added to the food-web outputs.
